Standalone Tactics using OpenTheory

### 2012-02-14 paper.tex
Final tweaks

We collected preliminary performance data for two test standalone tactics extracted from HOL4, and called from HOL Light.
They are QBF~\cite{DBLP:conf/itp/KumarW11}, which proves quantified boolean formulas, and SKICo, which rewrites terms to combinatory form, for example proving $\vdash(\forall{x}.\ x\,\lor\,\lnot x)=(\forall)\ (\mathtt{S}\ (\lor)\ (\lnot))$.
We used the following three test goals:
\begin{enumerate}
\item $\forall x.\ x \lor\lnot x$

>>>>

We collected preliminary performance data for two test standalone tactics extracted from HOL4, and called from HOL Light.
They are QBF~\cite{DBLP:conf/itp/KumarW11}, which proves quantified boolean formulas, and SKICo, which rewrites terms to combinatory form like so: $\vdash(\forall{x}.\ x\lor\lnot x)=(\forall)\ (\mathtt{S}\ (\lor)\ (\lnot))$.
We used the following three test goals:
\begin{enumerate}
\item $\forall x.\ x \lor\lnot x$
